Covariates analysis of MSBB RNASeq data

### 2016-01-22 code/Rmd/MSSM_RNASeq.Rmd
Added outlier analysis to the MSSM RNASeq workflow

# Initial design matrix with covariates under consideration
DM = getDesignMatrix(COVARIATES, Intercept = F)
```
### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
DESIGN = getDesignMat2Fact(DM$design,FactorCovariates)
rownames(DESIGN) = rownames(METADATA)
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, DESIGN,'NULL design(voom-normalized)', isKeyPlot=TRUE)

>>>>

# Initial design matrix with covariates under consideration
DM = getDesignMatrix(COVARIATES, Intercept = F)
```
### Outlier analysis
Clustering of initial normalised data (with NULL design)
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E, scale.=T)

# Plot first 2 PCs
plotdata <- data.frame(ID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'ID'))

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(TISSUE.Dx), shape=as.factor(CDR), size=as.numeric(PMI)))
p <- p + theme_bw() + theme(legend.position="top") + scale_shape_manual(values = 1:7)
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

tree = hclust(as.dist(t(VOOM.GENE_EXPRESSION$E)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
tmp = gsub('\\..*','',cols)
WGCNA::plotDendroAndColors(tree, 
                           colors = tmp, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
DESIGN = getDesignMat2Fact(DM$design,FactorCovariates)
rownames(DESIGN) = rownames(METADATA)
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, DESIGN,'NULL design(voom-normalized)', isKeyPlot=TRUE)
